\mytitle

### 2020-04-29 paper.tex
Edit to end of Sect 3.2

A benchmark study comparing state-of-the-art exact approaches \cite{Zhang2014} to 
approximate methods and found that the two perform in a comparable fashion, without large differences between
the attained energy~\cite{yang2019simulated}. Exact methods tend to perform slightly better
in smaller WFLO benchmarks, while simulated annealing methods dominated for larger standard WFLO benchmarks. 
These results lead to the conclusion that both types of methods (exact and approximate) should be considered and, therefore, we introduce a unified paradigm, namely quadratic programming, that enables
both exact and approximate solutions to WFLO. Further, formulating WFLO using quadratic programming enables us to employ 
recent advanced exact software solutions (e.g., Gurobi optimizer) and approximate hardware developments 
(e.g., Fujitsu's Digital Annealer).
%Thus, 
%our approach `enjoys' the best of both worlds (the exact and the approximate).

@@

Let $u_{id}$ and $u_{id\infty}$ 
be the wind speeds at turbine location $i \in \mathcal{N}$ for wind regime $d \in \mathcal{D}$
with and without interference from other turbines due to wake effects, respectively. 
Note that here we refer to $i$ as a potential turbine location and not the $i$th turbine as we did in Section~\ref{sec:related}.
Further, we denote by $\mathcal{U}_{id} \subseteq \mathcal{N}$ 
the set of upstream 
turbine locations for wind regime $d$
given that a turbine is placed at cell $i$ (i.e., turbines placed in these locations 
will influence a turbine placed in $i$). Finally,
we denote by $u_{ijd}$ the wind speed at location $j$ due to a single wake from upstream turbine at location $i$ with $j \in \mathcal{U}_{id}$. 
The following function  
represents the total expected energy of a wind farm given placement decisions 
$x$: \begin{equation}
f(x) = \sum_{i \in \mathcal{N}}^{} \sum_{d \in \mathcal{D}}^{} p_d ( \frac{1}{3} \ u_{id, \infty}^3 x_i  - \sum_{j \in \mathcal{U}_{id}}^{} \frac{1}{3}(u_{id, \infty} ^3 - u_{ijd}^3)x_i x_j).   \label{ObjFunc}\\
%&s.t.:& \nonumber\\
%&\mbox{       }& \sum_{i \in \mathcal{N}}^{} x_i = m,\label{Cardinality}\\
%&\mbox{       }& x_i + x_j \leq 1,   \forall (i,j) \in \mathcal{E}, \label{Grid}\\
%&\mbox{       }& x_i \in \{0,1\},     \forall i \in \mathcal{N}.
\end{equation} The objective function corresponds to the linear superposition (LS)
expression (c.f., Eq.~\ref{eq:ls} in Section~\ref{sec:related}). We are now ready to provide the two quadratic programs to represent WFLO.

@@

WFL-QCOP can be solved using an exact optimization solver, e.g., Gurobi~\cite{gurobi}. 
Similar, linear formulations have been previously proposed and solved using exact solvers~\cite{Zhang2014,donovan2005wind}. \todo{Are these linear formulations ``equivalent'' as you claimed or approximations? If they are mathematically equivalent, why do we think a quadratic model will be any better computationally? Arik: The two formulations are equivalent to WFL-QCOP. However, we compare against the ILP model experimentally and it does worse than WFL-QCOP. Hopefully, Jason's part in Section 3.5.1. based on Wen-Yang's thesis will explain why it does better. Originally, I used the quadratic formulation because it seemed more natural. Semantically, the linear model and the quadratic model are the equivalent imho.}

>>>>

A benchmark study comparing state-of-the-art exact approaches \cite{Zhang2014} to 
approximate methods and found that the two perform in a comparable fashion, without large differences between
the attained energy~\cite{yang2019simulated}. Exact methods tend to perform slightly better
in smaller WFLO benchmarks, while simulated annealing methods dominated for larger standard WFLO benchmarks. 
These results lead to the conclusion that both types of methods (exact and approximate) should be considered. Therefore, we introduce a unified paradigm, namely quadratic programming, that enables
both exact and approximate solutions to WFLO. Further, formulating WFLO using quadratic programming enables us to employ 
recent advanced exact software solutions (e.g., Gurobi optimizer) and approximate hardware developments 
(e.g., Fujitsu's Digital Annealer).
%Thus, 
%our approach `enjoys' the best of both worlds (the exact and the approximate).

@@

Let $u_{id}$ and $u_{id\infty}$ 
be the wind speeds at turbine location $i \in \mathcal{N}$ for wind regime $d \in \mathcal{D}$
with and without interference from other turbines due to wake effects, respectively. 
Note that here we refer to $i$ as a potential turbine location and not the $i$th turbine as we did in Section~\ref{sec:related}.\todo{JCB: This is an unnecessary change. Go back and reformulate Section~\ref{sec:related} to refer to the potential position $i$ rather than turbine $i$ so that we do not have this inconsistency.}
Further, we denote by $\mathcal{U}_{id} \subseteq \mathcal{N}$ 
the set of upstream 
turbine locations for wind regime $d$
given that a turbine is placed at cell $i$ (i.e., turbines placed in these locations 
will influence a turbine placed in $i$). Finally,
we denote by $u_{ijd}$ the wind speed at location $j$ due to a single wake from upstream turbine at location $i$ with $j \in \mathcal{U}_{id}$. 
The following function  
represents the total expected energy of a wind farm given placement decisions 
$x$: \begin{equation}
f(x) = \sum_{i \in \mathcal{N}}^{} \sum_{d \in \mathcal{D}}^{} p_d ( \frac{1}{3} \ u_{id, \infty}^3 x_i  - \sum_{j \in \mathcal{U}_{id}}^{} \frac{1}{3}(u_{id, \infty} ^3 - u_{ijd}^3)x_i x_j).   \label{ObjFunc}\\
%&s.t.:& \nonumber\\
%&\mbox{       }& \sum_{i \in \mathcal{N}}^{} x_i = m,\label{Cardinality}\\
%&\mbox{       }& x_i + x_j \leq 1,   \forall (i,j) \in \mathcal{E}, \label{Grid}\\
%&\mbox{       }& x_i \in \{0,1\},     \forall i \in \mathcal{N}.
\end{equation} The objective function corresponds to the linear superposition (LS)
expression (c.f., Eq.~\ref{eq:ls} in Section~\ref{sec:related}). We are now ready to provide the two quadratic programs to represent WFLO.

@@

WFL-QCOP can be solved using an exact optimization solver, e.g., Gurobi~\cite{gurobi}. 
Similar, linear formulations have been previously proposed and solved using exact solvers~\cite{Zhang2014,donovan2005wind}.
\todo{JCB: We need to formally present the ILP model in the experiment section. We can then discuss the fact that the model is identical - because the linearization gives and exact representation.}
%\todo{Are these linear formulations ``equivalent'' as you claimed or approximations? If they are mathematically equivalent, why do we think a quadratic model will be any better computationally? Arik: The two formulations are equivalent to WFL-QCOP. However, we compare against the ILP model experimentally and it does worse than WFL-QCOP. Hopefully, Jason's part in Section 3.5.1. based on Wen-Yang's thesis will explain why it does better. Originally, I used the quadratic formulation because it seemed more natural. Semantically, the linear model and the quadratic model are the equivalent imho.}
